### 2017-04-11 document/ms.tex
The document section contains the stub of a manuscript with data analysis details

\documentclass[twocolumn]{emulateapj}% change onecolumn to iop for fancy, iop

\let\pwiflocal=\iffalse \let\pwifjournal=\iffalse
\input{mgs_setup}

\newcommand{\iancze}{{\sc C15}}

\providecommand{\eprint}[1]{\href{http://arxiv.org/abs/#1}{#1}}
\providecommand{\adsurl}[1]{\href{#1}{ADS}}
\newcommand{\project}[1]{\textsl{#1}}

\slugcomment{In preparation}
\shorttitle{Class 0 near-IR spectroscopy}
\shortauthors{TBD}

\bibliographystyle{yahapj}

\begin{document}

\title{Near infrared spectrum of a Class 0 protostar photosphere}

\author{T.B. Determined,\altaffilmark{1}}

\altaffiltext{1}{NASA Ames}

\begin{abstract}
We measure the stellar photosphere of a Class 0 protostar.
\end{abstract}

\keywords{stars: fundamental parameters --- stars: individual (S68N) ---  stars: low-mass -- stars: statistics}

\maketitle

\section{Introduction}\label{sec:intro}
The method is from \citep{czekala16}.  It is similar to \citep{2017ApJ...836..200G}.

\subsection{Protostars}
\subsection{Previous studies of protostar photospheres}
\subsection{Previous studies of S68N}

\section{Observations}
The observations of S68N were carried out with NIRSPEC on the Keck telescope over 5 epochs from 2003-2014.  The \texttt{NIRSPEC-7} filter provided 1.84$-$2.63 $\mu$m wavelength range, with native spectral resolution of $R=1250$ from a 0\farcs76 (4 pixels) $\times$ 42\farcs0 slit.  
The individual epochs were coadded to form a single composite spectrum of signal to noise ratio $S/N\sim30$.

\section{Method}

Our approach involves Bayesian forward modeling of the observed spectrum under a range of different assumptions about the prostellar system.  We discuss the limitations of our assumptions in the discussion section.

\subsection{Composite spectrum forward model}

We assume that stellar photosphere and warm circumstellar disk emission dominate the radiation in the near-IR band.  We constructed a forward model for the observed Keck spectrum using the spectral inference framework \texttt{Starfish} from \citet{czekala16} with support for mixture model modifications from \citet{2017ApJ...836..200G}.  The mixture model for S68N's Keck spectrum is:

\begin{eqnarray} \label{eqn:mix_M}
	S_{\mathrm{mix}} = \Omega_{\mathrm{\star}} B(\teffa)  + \Omega_{\mathrm{d}} B(\teffb)
\end{eqnarray}
where $B(T)$ is the spectral radiance as a function of temperature.  The ratio of solid angles relates the relative size of the emission regions:
\begin{eqnarray} \label{eqn:fill_factor}
	\frac{\Omega_d}{\Omega_\star} = \frac{r_d^2 d^2}{r_\star^2 d^2} = \frac{r_d^2}{r_\star^2}
\end{eqnarray}

approximating the circumstellar disk emission as a face-on circle.  More accurate estimates for the disk emission and geometries could be obtained from rigorous radiative transfer methods \citep[\emph{e.g.}]{2017arXiv170305765R}.  We model the protostellar spectral radiance $B(T_\star)$ with \PHOENIX\ synthetic model spectra possessing an unknown-but-low surface gravity $\logg \in [2.0,4.0]$ in cm$/$s$^2$ and an effective temperature $\teffa \in [2700,3600]$ K.  The circumstellar disk radiance is assumed to be black body, with a temperature range $\teffb \in [1000,1700]$ K capped by the temperature at which typical dust sublimates.

The radiated spectrum passes through an unknown amount of extinction and scattering, altering its spectral shape in an uncertain---and assumed irretrievable---way.  So instead of characterizing the spectral slope by a reddening law and extinction, $A_V$, we instead assume that the overall spectral shape is approximated by a third order polynomial \footnote{The polynomial is parameterized as a linear combination of Chebyshev polynomials truncated to the first 3 non-constant terms.}.

We assume there is zero emission attributable to mass accretion onto the star or disk.  This assumption almost certainly fails for Class 0 protostars, which are still actively accreting a large fraction of their mass.  However, the dearth of any conspicuous emission lines suggests that perhaps the S68N is going through a quiescent phase in a variable accretion history.  In any case, the limited spectral information available does not permit a more detailed treatment of accretion or disk gas emission as is possible with higher spectral resolution \citep[\emph{e.g.}]{2016ApJ...826..179L}.

\subsection{Experiments}
 We tried several experiments:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TABLE - Experiment log
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{deluxetable*}{ccp{9cm}p{5cm}}

\tabcolsep=0.11cm
%\rotate
\tablecaption{Exeriment log \label{tbl_history}}
\tablewidth{0pt}
\tablehead{
\colhead{Exp.} &
\colhead{Run.} &
\colhead{Desc.} &
\colhead{Outcome}
\\
\colhead{\#} &
\colhead{\#} &
\colhead{-} &
\colhead{-}
}
\startdata
 1 & 1 & Original, flawed \texttt{star\_veil.py} code modeled disk radiance as a constant value with no physical interpretation & Exposed need for more physical inputs \\
2 & 1 & Run with \texttt{star\_BB.py} code with erroneous $\Omega$ prescription, weak priors, poor first guess & Exposed need for better priors and starting guess \\
2 & 2 & Run with \texttt{star\_BB.py} code with erroneous $\Omega$ prescription, strong priors ($T_{d}$ fixed to $\sim1100$ K), good first guess & Exposed incorrect $\Omega$ treatment \\
3 & 1 & Run with \texttt{star\_BB.py} code with correct absolute flux level, strong priors ($T_{d}$ fixed to $\sim1100$ K). & Reasonable results, weak constraints on $\logg$. \\
3 & 2 & \emph{In progress:} Run with \texttt{star\_BB.py} code with correct absolute flux level, \emph{weak} priors ($T_{d}$ variable $\in [1000,1700]$ K). & -- \\
4 & 1 & Reduced spectral range to enhance $\logg$ sensitivity & Good convergence, wide range \\
\enddata
\end{deluxetable*}

\section{Results}

\subsection{Experiment 3, Run 1}

\begin{figure}
 \centering
 \includegraphics[width=0.45\textwidth]{../plots/logg_omega_phys.pdf}
 \caption{Posterior probability distribution function from Experiment 3, Run1, marginalized over all stellar and nuisance parameters except $\logg$ and $\Omega_d/\Omega_\star$.  The surface gravity correlates with the solid angle ratio since both of these factors affect the CO line depths.  Lines of differing stellar mass and disk radii are shown for a range of stellar radii.}
 \label{fig:posterior_loggOmega}
\end{figure}

~\clearpage

\begin{figure*}[b]
 \centering
 \includegraphics[width=0.85\textwidth]{../plots/gully_Class0_Teff_logg_results.pdf}
 \caption{Pre-main sequence and protostar evolution comparison between theory (left panel) and obseration (right panel).  The 0.02$-$1.2 $M_{\odot}$ evolutionary model tracks are from \citet{baraffe15}, spanning 1 Myr to 100 Myr isochrones; protostars are expected to sit below the 1 Myr isochrone in the region of parameter space demarcated with a yellow dashed ellipse.  The observations show coarse agreement with the models-- measurements of the Pleiades from \citet[green KDE]{cottaar14} cluster around the 100 Myr isochrone, although extend into higher-than-predicted $\log{g}$ for hotter stars.  The younger IC348 sources \citep[purple KDE]{cottaar14} cluster with a large spread above and below the $\sim10$ Myr isochrone.  The source S 68N has a broad posterior PDF (Experiment 4-teal KDE, Experiment 3- red/brown KDE) placing its maximum a-posteriori estimate inside the range of protostars, regardless of experimental assumptions.  The black dots are Class I protostars from \citet{2005AJ....130.1145D}, showing a large range in measured properties with relatively large uncertainties in $\log{g}$.}  
 \label{fig:theory_v_obs}
\end{figure*}

\section{Discussion}

\clearpage
\pagebreak

\appendix

\section{Adaptations of Starfish to handle absolute flux and solid angle}

\acknowledgements
We thank the Keck telescope staff.

{\it Facilities:} \facility{Keck (NIRSPEC)}

{\it Software: } 
 \project{pandas} \citep{mckinney10},
 \project{emcee} \citep{foreman13},
 \project{matplotlib} \citep{hunter07},
 \project{numpy} \citep{vanderwalt11},
 \project{scipy} \citep{jones01},
 \project{ipython} \citep{perez07},
 \project{starfish} \citep{czekala15},
 \project{seaborn} \citep{waskom14}

\clearpage

\bibliographystyle{apj}
\bibliography{ms}

\end{document}

### 2017-04-12 code/model_BB.py
Experiment with custom star.py scripts being housed in individual project code/ repos

@@ -1,0 +1,155 @@
+import numpy as np
+import Starfish
+from . import constants as C
+from .grid_tools import Interpolator
+import json
+import h5py
+import logging
+import matplotlib.pyplot as plt
+from itertools import zip_longest
+
+def grouper(iterable, n, fillvalue=None):
+    "Collect data into fixed-length chunks or blocks"
+    # grouper('ABCDEFG', 3, 'x') --> ABC DEF Gxx"
+    args = [iter(iterable)] * n
+    return zip_longest(*args, fillvalue=fillvalue)
+
+class ThetaParam:
+    '''
+    An object holding the collection of parameters shared between all orders.
+
+    :param grid: parameters corresponding to the dimensions of the grid.
+    :type grid: 1D np.array
+    '''
+    def __init__(self, grid, vz=0.0, vsini=0.0, logOmega=0.0, Av=0.0, T_BB=1100.0, logOmega2=0.0):
+        self.grid = grid
+        self.vz = vz
+        self.vsini = vsini
+        self.logOmega = logOmega #log10Omega
+        self.Av = Av
+        self.T_BB = T_BB
+        self.logOmega2 = logOmega2 #log10Omega
+
+    def save(self, fname="theta.json"):
+        '''
+        Save the parameters to a JSON file
+        '''
+        f = open(fname, 'w')
+        json.dump(self, f, cls=ThetaEncoder, indent=2, sort_keys=True)
+        f.close()
+
+    @classmethod
+    def from_dict(cls, d):
+        '''
+        Load the parameters from a dictionary, e.g., from the config file
+
+        :param d: dictionary of parameters
+        :type d: dictionary
+        '''
+        d["grid"] = np.array(d["grid"])
+        return cls(**d)
+
+    @classmethod
+    def load(cls, fname="theta.json"):
+        '''
+        Load the parameters from a JSON file
+        '''
+        f = open(fname, "r")
+        read = json.load(f) # read is a dictionary
+        f.close()
+        read["grid"] = np.array(read["grid"])
+        return cls(**read)
+
+    def __repr__(self):
+        return "grid:{} vz:{} vsini:{} logOmega:{} Av:{} T_BB:{} logOmega2:{}".format(self.grid, self.vz, self.vsini, self.logOmega, self.Av, self.T_BB, self.logOmega2)
+
+class ThetaEncoder(json.JSONEncoder):
+    '''
+    Serialize an instance of o=ThetaParam() to JSON
[…]

### 2017-04-12 code/star_BB.py

@@ -1,0 +1,490 @@
+#!/usr/bin/env python
+
+# All of the argument parsing is done in the `parallel.py` module.
+
+import multiprocessing
+import time
+import numpy as np
+import Starfish
+from Starfish.model_BB import ThetaParam, PhiParam
+
+import argparse
+parser = argparse.ArgumentParser(prog="star_BB.py", description="Run Starfish fitting model in single order mode with many walkers, with extra black body component.")
+parser.add_argument("--samples", type=int, default=5, help="How many samples to run?")
+parser.add_argument("--incremental_save", type=int, default=100, help="How often to save incremental progress of MCMC samples.")
+parser.add_argument("--resume", action="store_true", help="Continue from the last sample. If this is left off, the chain will start from your initial guess specified in config.yaml.")
+args = parser.parse_args()
+
+import os
+
+import Starfish.grid_tools
+from Starfish.spectrum import DataSpectrum, Mask, ChebyshevSpectrum
+from Starfish.emulator import Emulator
+import Starfish.constants as C
+from Starfish.covariance import get_dense_C, make_k_func, make_k_func_region
+
+from scipy.special import j1
+from scipy.interpolate import InterpolatedUnivariateSpline
+from scipy.linalg import cho_factor, cho_solve
+from numpy.linalg import slogdet
+from astropy.stats import sigma_clip
+from astropy.analytic_functions import blackbody_lambda
+from astropy import units as u
+
+import gc
+import logging
+
+from itertools import chain
+#from collections import deque
+from operator import itemgetter
+import yaml
+import shutil
+import json
+
+
+
+Starfish.routdir = ""
+
+# list of keys from 0 to (norders - 1)
+order_keys = np.arange(1)
+DataSpectra = [DataSpectrum.open(os.path.expandvars(file), orders=Starfish.data["orders"]) for file in Starfish.data["files"]]
+# list of keys from 0 to (nspectra - 1) Used for indexing purposes.
+spectra_keys = np.arange(len(DataSpectra))
+
+#Instruments are provided as one per dataset
+Instruments = [eval("Starfish.grid_tools." + inst)() for inst in Starfish.data["instruments"]]
+
+logging.basicConfig(format="%(asctime)s - %(levelname)s - %(name)s -  %(message)s", filename="{}log.log".format(
+    Starfish.routdir), level=logging.DEBUG, filemode="w", datefmt='%m/%d/%Y %I:%M:%S %p')
+
+class Order:
[…]

### 2017-04-12 code/model_BB.py
Change absolute and relative imports so that the star.py script finds the local model.py, and model.py finds the global grid tools.

@@ -1,7 +1,7 @@
 import numpy as np
 import Starfish
-from . import constants as C
-from .grid_tools import Interpolator
+from Starfish import constants as C
+from Starfish.grid_tools import Interpolator
 import json
 import h5py
 import logging

### 2017-04-12 code/star_protostars.py

@@ -6,7 +6,7 @@ import multiprocessing
 import time
 import numpy as np
 import Starfish
-from Starfish.model_BB import ThetaParam, PhiParam
+from model_BB import ThetaParam, PhiParam
 
 import argparse
 parser = argparse.ArgumentParser(prog="star_BB.py", description="Run Starfish fitting model in single order mode with many walkers, with extra black body component.")

### 2017-04-12 code/star_protostars_Av.py
Experiment to include extinction

@@ -1,0 +1,490 @@
+#!/usr/bin/env python
+
+# All of the argument parsing is done in the `parallel.py` module.
+
+import multiprocessing
+import time
+import numpy as np
+import Starfish
+from model_BB import ThetaParam, PhiParam
+
+import argparse
+parser = argparse.ArgumentParser(prog="star_BB.py", description="Run Starfish fitting model in single order mode with many walkers, with extra black body component.")
+parser.add_argument("--samples", type=int, default=5, help="How many samples to run?")
+parser.add_argument("--incremental_save", type=int, default=100, help="How often to save incremental progress of MCMC samples.")
+parser.add_argument("--resume", action="store_true", help="Continue from the last sample. If this is left off, the chain will start from your initial guess specified in config.yaml.")
+args = parser.parse_args()
+
+import os
+
+import Starfish.grid_tools
+from Starfish.spectrum import DataSpectrum, Mask, ChebyshevSpectrum
+from Starfish.emulator import Emulator
+import Starfish.constants as C
+from Starfish.covariance import get_dense_C, make_k_func, make_k_func_region
+
+from scipy.special import j1
+from scipy.interpolate import InterpolatedUnivariateSpline
+from scipy.linalg import cho_factor, cho_solve
+from numpy.linalg import slogdet
+from astropy.stats import sigma_clip
+from astropy.analytic_functions import blackbody_lambda
+from astropy import units as u
+
+import gc
+import logging
+
+from itertools import chain
+#from collections import deque
+from operator import itemgetter
+import yaml
+import shutil
+import json
+
+
+
+Starfish.routdir = ""
+
+# list of keys from 0 to (norders - 1)
+order_keys = np.arange(1)
+DataSpectra = [DataSpectrum.open(os.path.expandvars(file), orders=Starfish.data["orders"]) for file in Starfish.data["files"]]
+# list of keys from 0 to (nspectra - 1) Used for indexing purposes.
+spectra_keys = np.arange(len(DataSpectra))
+
+#Instruments are provided as one per dataset
+Instruments = [eval("Starfish.grid_tools." + inst)() for inst in Starfish.data["instruments"]]
+
+logging.basicConfig(format="%(asctime)s - %(levelname)s - %(name)s -  %(message)s", filename="{}log.log".format(
+    Starfish.routdir), level=logging.DEBUG, filemode="w", datefmt='%m/%d/%Y %I:%M:%S %p')
+
+class Order:
+    def __init__(self, debug=False):
[…]

### 2017-05-02 code/model_BB_varA_K.py
Allow power law exponent to vary with range of values consistent with near-IR extinction.  Closes #18.

@@ -1,0 +1,25 @@
+from model_BB import *
+from model_BB import ThetaParam as ThetaParamBase
+
+
+class ThetaParam(ThetaParamBase):
+    '''
+    Inherit the base model and extend it to include an extra parameter: scattering
+
+    :param grid: parameters corresponding to the dimensions of the grid.
+    :type grid: 1D np.array
+    '''
+    def __init__(self, grid, vz=0.0, vsini=0.0, logOmega=0.0, A_K=0.0, T_BB=1100.0, logOmega2=0.0, exponentA_K=-1.999):
+        self.grid = grid
+        self.vz = vz
+        self.vsini = vsini
+        self.logOmega = logOmega #log10Omega
+        self.T_BB = T_BB
+        self.logOmega2 = logOmega2 #log10Omega2
+        #Ignore Av-- we are using A_K instead
+        self.exponentA_K = exponentA_K
+        self.A_K = A_K
+
+    def __repr__(self):
+        return "grid:{} vz:{} vsini:{} logOmega:{} A_K:{} T_BB:{} logOmega2:{} exponentA_K:{}".format(self.grid,
+         self.vz, self.vsini, self.logOmega, self.A_K, self.T_BB, self.logOmega2, self.exponentA_K)

### 2017-05-02 code/model_BB_varAv.py

@@ -1,0 +1,18 @@
+from model_BB import *
+from model_BB import ThetaParam as ThetaParamBase
+
+
+class ThetaParam(ThetaParamBase):
+    '''
+    Inherit the base model and extend it to include an extra parameter: scattering
+
+    :param grid: parameters corresponding to the dimensions of the grid.
+    :type grid: 1D np.array
+    '''
+    def __init__(self, grid, vz=0.0, vsini=0.0, logOmega=0.0, Av=0.0, T_BB=1100.0, logOmega2=0.0, exponentAv=-2.0):
+        ThetaParamBase.__init__(self, grid, vz, vsini, logOmega, Av, T_BB, logOmega2)
+        self.exponentAv = exponentAv
+
+    def __repr__(self):
+        return "grid:{} vz:{} vsini:{} logOmega:{} Av:{} T_BB:{} logOmega2:{} exponentAv:{}".format(self.grid,
+         self.vz, self.vsini, self.logOmega, self.Av, self.T_BB, self.logOmega2, self.exponentAv)

### 2017-05-02 code/star_protostars_varA_K.py

@@ -1,0 +1,227 @@
+#!/usr/bin/env python
+import time
+import numpy as np
+import argparse
+parser = argparse.ArgumentParser(prog="star_protostars_varA_K.py", description="Run Starfish fitting model in single order mode with many walkers, with extra black body component, and variable A_K exponent")
+parser.add_argument("--samples", type=int, default=5, help="How many samples to run?")
+parser.add_argument("--incremental_save", type=int, default=100, help="How often to save incremental progress of MCMC samples.")
+parser.add_argument("--resume", action="store_true", help="Continue from the last sample. If this is left off, the chain will start from your initial guess specified in config.yaml.")
+args = parser.parse_args()
+
+import os
+
+import multiprocessing
+import Starfish.grid_tools
+from Starfish.spectrum import DataSpectrum, Mask, ChebyshevSpectrum
+from Starfish.emulator import Emulator
+import Starfish.constants as C
+from Starfish.covariance import get_dense_C, make_k_func, make_k_func_region
+from numpy.polynomial import Chebyshev as Ch
+
+from scipy.special import j1
+from scipy.interpolate import InterpolatedUnivariateSpline
+from scipy.linalg import cho_factor, cho_solve
+from numpy.linalg import slogdet
+from astropy.stats import sigma_clip
+from astropy.analytic_functions import blackbody_lambda
+from astropy import units as u
+
+import gc
+import logging
+
+from itertools import chain
+#from collections import deque
+from operator import itemgetter
+import yaml
+import shutil
+import json
+
+from star_base import Order as OrderBase
+from star_base import SampleThetaPhi as SampleThetaPhiBase 
+from model_BB_varA_K import ThetaParam, PhiParam
+
+Starfish.routdir = ""
+
+# list of keys from 0 to (norders - 1)
+order_keys = np.arange(1)
+DataSpectra = [DataSpectrum.open(os.path.expandvars(file), orders=Starfish.data["orders"]) for file in Starfish.data["files"]]
+# list of keys from 0 to (nspectra - 1) Used for indexing purposes.
+spectra_keys = np.arange(len(DataSpectra))
+
+#Instruments are provided as one per dataset
[…]

### 2017-05-02 code/star_protostars_varAv.py

@@ -1,0 +1,222 @@
+#!/usr/bin/env python
+import time
+import numpy as np
+import argparse
+parser = argparse.ArgumentParser(prog="star_protostars_varAv.py", description="Run Starfish fitting model in single order mode with many walkers, with extra black body component, and variable Av exponent")
+parser.add_argument("--samples", type=int, default=5, help="How many samples to run?")
+parser.add_argument("--incremental_save", type=int, default=100, help="How often to save incremental progress of MCMC samples.")
+parser.add_argument("--resume", action="store_true", help="Continue from the last sample. If this is left off, the chain will start from your initial guess specified in config.yaml.")
+args = parser.parse_args()
+
+import os
+
+import multiprocessing
+import Starfish.grid_tools
+from Starfish.spectrum import DataSpectrum, Mask, ChebyshevSpectrum
+from Starfish.emulator import Emulator
+import Starfish.constants as C
+from Starfish.covariance import get_dense_C, make_k_func, make_k_func_region
+from numpy.polynomial import Chebyshev as Ch
+
+from scipy.special import j1
+from scipy.interpolate import InterpolatedUnivariateSpline
+from scipy.linalg import cho_factor, cho_solve
+from numpy.linalg import slogdet
+from astropy.stats import sigma_clip
+from astropy.analytic_functions import blackbody_lambda
+from astropy import units as u
+
+import gc
+import logging
+
+from itertools import chain
+#from collections import deque
+from operator import itemgetter
+import yaml
+import shutil
+import json
+
+from star_base import Order as OrderBase
+from star_base import SampleThetaPhi as SampleThetaPhiBase 
+from model_BB_varAv import ThetaParam, PhiParam
+
+Starfish.routdir = ""
+
+# list of keys from 0 to (norders - 1)
+order_keys = np.arange(1)
+DataSpectra = [DataSpectrum.open(os.path.expandvars(file), orders=Starfish.data["orders"]) for file in Starfish.data["files"]]
+# list of keys from 0 to (nspectra - 1) Used for indexing purposes.
+spectra_keys = np.arange(len(DataSpectra))
+
+#Instruments are provided as one per dataset
[…]

### 2017-05-04 document/ms.tex
Update the ms table with description of experiments

@@
 3 & 1 & Run with \texttt{star\_BB.py} code with correct absolute flux level, strong priors ($T_{d}$ fixed to $\sim1100$ K). & Reasonable results, weak constraints on $\logg$. \\
-3 & 2 & \emph{In progress:} Run with \texttt{star\_BB.py} code with correct absolute flux level, \emph{weak} priors ($T_{d}$ variable $\in [1000,1700]$ K). & -- \\
-4 & 1 & Reduced spectral range to enhance $\logg$ sensitivity & Good convergence, wide range \\
+3 & 2 & Run with \texttt{star\_BB.py} code with correct absolute flux level, \emph{weak} priors ($T_{d}$ variable $\in [1000,1700]$ K). & -- \\
+4 & 1 & Reduced spectral range to enhance $\logg$ sensitivity & Good convergence, wide posteriors \\
+5 & 1 &  Windowing on CO and Na~I, $T_{d}$ fixed to $\sim1100$ K & Slightly higher $T_{\mathrm{eff}}$ and $\log{g}$ compared to just CO window.\\
+6 & 1 &  Introduce $A_V$, with fixed ($\chi=-2.0$) slope, $\log{g}>2.0$, Chebyshev $6\%$ peak-to-valley & Tighter $T_{eff}$ and $\log{g}$ posteriors than before\\
+7 & 1 &  $A_V$, with variable ($\chi \in [-2.0, -1.7]$) slope, $\log{g}>2.0$, Chebyshev $2\%$ peak-to-valley & Tighter $T_{eff}$ and $\log{g}$ posteriors due to tighter Chebyshev, $\chi$ limit exceeded\\
+8 & 1 &  $A_K$, with variable ($\chi \in [-2.0, -1.7]$) slope, $\log{g}>2.0$, Chebyshev $2\%$ peak-to-valley & Re-running\\
 \enddata

### 2017-05-04 sf/exp7/user_prior.py
Add all recent Starfish config.yaml files, phi initialization files, and most posterior emcee MCMC numpy save files

@@ -1,0 +1,28 @@
+def user_defined_lnprior(p):
+    '''
+    Takes a vector of stellar parameters and returns the ln prior.
+    '''
+    if not ( (p[2] < 0.5) and (p[2] > 0) and
+             (p[3] < 1000.0) and (p[3] > -1000.0) and
+             (p[4] < 500.0) and (p[4] > 2.0) and
+             (p[6] < 1500.0) and (p[6] > 1000.0) and
+             (p[8] < 100.0) and (p[8] > 0.0) and
+             (p[9] < -1.7) and (p[9] > -2) and
+             (p[13] > 0.0) and (p[13] < 2.0) and
+             (p[14] < -1.0) and (p[14] > -2.0) and
+             (p[15] > 0.0) and (p[15] < 300 ) ):
+
+    	return -np.inf
+    
+    # Solar metalicity to within +/- 0.05 dex
+    lnp_FeH = -1.0*(p[2] - 0.01)**2/(2.0*0.001**2)
+    lnp_vz = -1.0*(p[3] - 110.0)**2/(2.0*20.0**2)
+    lnp_vsini = -1.0*(p[4] - 105.1)**2/(2.0*30.0**2)
+    lnp_l = -1.0*(p[15] - 124.4)**2/(2.0*10.0**2)
+    lnp_logAmp = -1.0*(p[14] + 1.40)**2/(2.0*0.03**2)
+    lnp_T_BB = -1.0*(p[6] - 1100.0)**2/(2.0*10.0**2)
+    # No prior on v_z.
+    ln_prior_out = lnp_FeH + lnp_vz + lnp_vsini + lnp_l + lnp_logAmp + lnp_T_BB
+
+    return ln_prior_out
+

### 2017-05-04 sf/exp8/user_prior.py

@@ -1,0 +1,27 @@
+def user_defined_lnprior(p):
+    '''
+    Takes a vector of stellar parameters and returns the ln prior.
+    '''
+    if not ( (p[2] < 0.5) and (p[2] > 0) and
+             (p[3] < 1000.0) and (p[3] > -1000.0) and
+             (p[4] < 500.0) and (p[4] > 2.0) and
+             (p[6] < 1500.0) and (p[6] > 1000.0) and
+             (p[8] < 20.0) and (p[8] > 0.0) and
+             (p[9] < -1.7) and (p[9] > -2) and
+             (p[13] > 0.0) and (p[13] < 2.0) and
+             (p[14] < -1.0) and (p[14] > -3.0) and
+             (p[15] > 0.0) and (p[15] < 300 ) ):
+
+    	return -np.inf
+    
+    # Solar metalicity to within +/- 0.05 dex
+    lnp_FeH = -1.0*(p[2] - 0.01)**2/(2.0*0.001**2)
+    lnp_vz = -1.0*(p[3] - 110.0)**2/(2.0*20.0**2)
+    lnp_vsini = -1.0*(p[4] - 105.1)**2/(2.0*30.0**2)
+    lnp_l = -1.0*(p[15] - 124.4)**2/(2.0*10.0**2)
+    lnp_logAmp = -1.0*(p[14] + 1.40)**2/(2.0*0.03**2)
+    # No prior on v_z.
+    ln_prior_out = lnp_FeH + lnp_vz + lnp_vsini + lnp_l + lnp_logAmp
+
+    return ln_prior_out
+

### 2017-05-08 document/ms.tex
Update the ms and post the most recent pdf version of the ms.

--- 2017-04-11 document/ms.tex
@@
 
-The radiated spectrum passes through an unknown amount of extinction and scattering, altering its spectral shape in an uncertain---and assumed irretrievable---way.
-So instead of characterizing the spectral slope by a reddening law and extinction, $A_V$, we instead assume that the overall spectral shape is approximated by a third order polynomial \footnote{The polynomial is parameterized as a linear combination of Chebyshev polynomials truncated to the first 3 non-constant terms.}.
+The radiated spectrum passes through an unknown amount of extinction and scattering, altering its spectral shape in an uncertain---and potentially irretrievable---way.
+We explored several options for characterizing the extinction towards S68N.
+First, instead of characterizing the spectral slope by a reddening law and extinction, $A_V$, we instead assumed that the overall spectral shape is approximated by a third order polynomial \footnote{The polynomial is parameterized as a linear combination of Chebyshev polynomials truncated to the first 3 non-constant terms.}.
+The polynomial coefficients lacked interpretability, and may not have adequately approximated extinction power laws, so we also experimented with an $A_K$ and a power law slope:
+
+$$ A_\lambda / A_K = \frac{\lambda}{2.2 \; \mu\mathrm{m}}^\alpha$$
+
+with $\alpha \in [-2, -1.7]$ representing the power law exponent that may depend on dust properties and degree of extinction.
 
@@
 This assumption almost certainly fails for Class 0 protostars, which are still actively accreting a large fraction of their mass.
-However, the dearth of any conspicuous emission lines suggests that perhaps the S68N is going through a quiescent phase in a variable accretion history.
+We see H$_2$ emission lines in the $K-$band spectrum of S68N, so some degree of accretion is likely ongoing, potentially contributing non-negligible veiling in the photospheric absorption lines.
 In any case, the limited spectral information available does not permit a more detailed treatment of accretion or disk gas emission as is possible with higher spectral resolution \citep[\emph{e.g.}]{2016ApJ...826..179L}.
@@
 3 & 1 & Run with \texttt{star\_BB.py} code with correct absolute flux level, strong priors ($T_{d}$ fixed to $\sim1100$ K). & Reasonable results, weak constraints on $\logg$. \\
-3 & 2 & \emph{In progress:} Run with \texttt{star\_BB.py} code with correct absolute flux level, \emph{weak} priors ($T_{d}$ variable $\in [1000,1700]$ K). & -- \\
-4 & 1 & Reduced spectral range to enhance $\logg$ sensitivity & Good convergence, wide range \\
+3 & 2 & Run with \texttt{star\_BB.py} code with correct absolute flux level, \emph{weak} priors ($T_{d}$ variable $\in [1000,1700]$ K). & -- \\
+4 & 1 & Reduced spectral range to enhance $\logg$ sensitivity & Good convergence, wide posteriors \\
+5 & 1 &  Windowing on CO and Na~I, $T_{d}$ fixed to $\sim1100$ K & Slightly higher $T_{\mathrm{eff}}$ and $\log{g}$ compared to just CO window.\\
+6 & 1 &  Introduce $A_V$, with fixed ($\alpha=-2.0$) slope, $\log{g}>2.0$, Chebyshev $6\%$ peak-to-valley & Tighter $T_{eff}$ and $\log{g}$ posteriors than before\\
+7 & 1 &  $A_V$, with variable ($\alpha \in [-2.0, -1.7]$) slope, $\log{g}>2.0$, Chebyshev $2\%$ peak-to-valley & Tighter $T_{eff}$ and $\log{g}$ posteriors due to tighter Chebyshev, $\alpha$ limit exceeded\\
+8 & 1 &  $A_K$, with variable ($\alpha \in [-2.0, -1.7]$) slope, $\log{g}>2.0$, Chebyshev $2\%$ peak-to-valley & Re-running\\
 \enddata

### 2017-05-10 code/star_base.py
The self.ss[0] = 0.01 seems to be a bug that we need to turn off.

@@ -102,7 +102,7 @@ class Order:
         self.EIGENSPECTRA = np.vstack((self.pca.flux_mean[np.newaxis,:], self.pca.flux_std[np.newaxis,:], self.pca.eigenspectra))
 
         self.ss = np.fft.rfftfreq(self.pca.npix, d=self.emulator.dv)
-        self.ss[0] = 0.01 # junk so we don't get a divide by zero error
+        #self.ss[0] = 0.01 # junk so we don't get a divide by zero error
 
         # Holders to store the convolved and resampled eigenspectra
         self.eigenspectra = np.empty((self.pca.m, self.ndata))

### 2017-05-10 code/star_proto_varA_K_delR.py
Rebrand vsini as deltaR, the extra convolution with instrumental broadening kernel.

@@ -1,0 +1,300 @@
+#!/usr/bin/env python
+import time
+import numpy as np
+import argparse
+parser = argparse.ArgumentParser(prog="star_protostars_varA_K.py", description="Run Starfish fitting model in single order mode with many walkers, with extra black body component, and variable A_K exponent")
+parser.add_argument("--samples", type=int, default=5, help="How many samples to run?")
+parser.add_argument("--incremental_save", type=int, default=100, help="How often to save incremental progress of MCMC samples.")
+parser.add_argument("--resume", action="store_true", help="Continue from the last sample. If this is left off, the chain will start from your initial guess specified in config.yaml.")
+args = parser.parse_args()
+
+import os
+
+import multiprocessing
+import Starfish.grid_tools
+from Starfish.spectrum import DataSpectrum, Mask, ChebyshevSpectrum
+from Starfish.emulator import Emulator
+import Starfish.constants as C
+from Starfish.covariance import get_dense_C, make_k_func, make_k_func_region
+from numpy.polynomial import Chebyshev as Ch
+
+from scipy.special import j1
+from scipy.interpolate import InterpolatedUnivariateSpline
+from scipy.linalg import cho_factor, cho_solve
+from numpy.linalg import slogdet
+from astropy.stats import sigma_clip
+from astropy.analytic_functions import blackbody_lambda
+from astropy import units as u
+
+import gc
+import logging
+
+from itertools import chain
+#from collections import deque
+from operator import itemgetter
+import yaml
+import shutil
+import json
+
+from star_base import Order as OrderBase
+from star_base import SampleThetaPhi as SampleThetaPhiBase 
+from model_BB_varA_K import ThetaParamDelR as ThetaParam
+from model_BB_varA_K import PhiParam
+
+Starfish.routdir = ""
+
+# list of keys from 0 to (norders - 1)
+order_keys = np.arange(1)
+DataSpectra = [DataSpectrum.open(os.path.expandvars(file), orders=Starfish.data["orders"]) for file in Starfish.data["files"]]
+# list of keys from 0 to (nspectra - 1) Used for indexing purposes.
+spectra_keys = np.arange(len(DataSpectra))
+
+#Instruments are provided as one per dataset
[…]

### 2017-05-10 code/model_BB_varA_K.py
Issue #22: rebrand vsini as delR-- also, we should really remove the hardcoded jump sizes, and put that back into the config.yaml file.

@@ -23,3 +23,25 @@ class ThetaParam(ThetaParamBase):
     def __repr__(self):
         return "grid:{} vz:{} vsini:{} logOmega:{} A_K:{} T_BB:{} logOmega2:{} exponentA_K:{}".format(self.grid,
          self.vz, self.vsini, self.logOmega, self.A_K, self.T_BB, self.logOmega2, self.exponentA_K)
+
+class ThetaParamDelR(ThetaParamBase):
+    '''
+    Inherit the base model and extend it to include an extra parameter: scattering
+
+    :param grid: parameters corresponding to the dimensions of the grid.
+    :type grid: 1D np.array
+    '''
+    def __init__(self, grid, vz=0.0, delR=0.0, logOmega=0.0, A_K=0.0, T_BB=1100.0, logOmega2=0.0, exponentA_K=-1.999):
+        self.grid = grid
+        self.vz = vz
+        self.delR = delR
+        self.logOmega = logOmega #log10Omega
+        self.T_BB = T_BB
+        self.logOmega2 = logOmega2 #log10Omega2
+        #Ignore Av-- we are using A_K instead
+        self.exponentA_K = exponentA_K
+        self.A_K = A_K
+
+    def __repr__(self):
+        return "grid:{} vz:{} delR:{} logOmega:{} A_K:{} T_BB:{} logOmega2:{} exponentA_K:{}".format(self.grid,
+         self.vz, self.delR, self.logOmega, self.A_K, self.T_BB, self.logOmega2, self.exponentA_K)        

### 2017-05-10 code/star_protostars_varA_K.py

@@ -68,8 +68,7 @@ class Order(OrderBase):
         A_lambda_A_K =  (self.wl/22000.0)**p.exponentA_K #std law is -1.74, Nishiyama is -2.0
         total_extinction = 10**(-0.4 * p.A_K * A_lambda_A_K)
         self.extinction = total_extinction / np.mean(total_extinction) 
-        #self.sca_lambda = p.sca*(self.wl/10000.0/2.2)**-4.0 #Rayleigh Scattering
-
+        
 
     def evaluate(self):
         '''
@@ -195,7 +194,7 @@ p0 = np.array(start["grid"] + [start["vz"], start["vsini"], start["logOmega"], s
               start["logOmega2"], start["A_K"] , start["exponentA_K"]] +
              phi0.cheb.tolist() + [phi0.sigAmp, phi0.logAmp, phi0.l])
 
-p0_std = [5, 0.02, 0.0005, 0.5, 0.5, -0.01, 5, -0.01, 0.1, 0.0001, -0.005, -0.005, -0.005, 0.01, 0.001, 0.5]
+p0_std = [5, 0.02, 0.0005, 0.5, 0.5, 0.01, 5, 0.01, 0.01, 0.000001, 0.005, 0.005, 0.005, 0.01, 0.001, 0.5]
 
 if args.resume:
     p0_ball = np.load("emcee_chain.npy")[:,-1,:]

### 2017-05-15 document/ms.tex
Now also posting the ms.tex content to sharelatex

@@
 \section{Introduction}\label{sec:intro}
-The method is from \citep{czekala16}.  It is similar to \citep{2017ApJ...836..200G}.
+The method is from \citep{czekala15}.  It is similar to \citep{2017ApJ...836..200G}.
 
@@
 
-Our approach involves Bayesian forward modeling of the observed spectrum under a range of different assumptions about the prostellar system.
+Our approach involves Bayesian forward modeling of the observed spectrum under a range of different assumptions about the protostellar system.
 We discuss the limitations of our assumptions in the discussion section.
@@
 
-We assume that stellar photosphere and warm circumstellar disk emission dominate the radiation in the near-IR band.
-We constructed a forward model for the observed Keck spectrum using the spectral inference framework \texttt{Starfish} from \citet{czekala16} with support for mixture model modifications from \citet{2017ApJ...836..200G}.
+We assume that stellar photosphere and warm circumstellar disk emission dominate the radiation in the near-IR $K-$band.
+We constructed a forward model for the observed Keck spectrum using the spectral inference framework \texttt{Starfish} from \citet{czekala15} with support for mixture model modifications from \citet{2017ApJ...836..200G}.
 The mixture model for S68N's Keck spectrum is:
@@
 
-$$ A_\lambda / A_K = \frac{\lambda}{2.2 \; \mu\mathrm{m}}^\alpha$$
+$$ A_\lambda / A_K = \frac{\lambda}{2.2 \; \mu\mathrm{m}}^{-\alpha}$$
 
-with $\alpha \in [-2, -1.7]$ representing the power law exponent that may depend on dust properties and degree of extinction.
+with $\alpha \in [-2, -1.7]$ representing the power law exponent that may depend on dust properties and degree of extinction.  The extinction is then defined as:
+
+$$ 10^{-0.4 A_\lambda}$$
 

### 2017-05-15 code/star_proto_varA_K_delR_GMM.py
Code for Issue #23-- using a Gaussian Mixture Model prior

@@ -1,0 +1,317 @@
+#!/usr/bin/env python
+import time
+import numpy as np
+import argparse
+parser = argparse.ArgumentParser(prog="star_protostars_varA_K.py", description="Run Starfish fitting model in single order mode with many walkers, with extra black body component, and variable A_K exponent")
+parser.add_argument("--samples", type=int, default=5, help="How many samples to run?")
+parser.add_argument("--incremental_save", type=int, default=100, help="How often to save incremental progress of MCMC samples.")
+parser.add_argument("--resume", action="store_true", help="Continue from the last sample. If this is left off, the chain will start from your initial guess specified in config.yaml.")
+args = parser.parse_args()
+
+import os
+
+import multiprocessing
+import Starfish.grid_tools
+from Starfish.spectrum import DataSpectrum, Mask, ChebyshevSpectrum
+from Starfish.emulator import Emulator
+import Starfish.constants as C
+from Starfish.covariance import get_dense_C, make_k_func, make_k_func_region
+from numpy.polynomial import Chebyshev as Ch
+
+from scipy.special import j1
+from scipy.interpolate import InterpolatedUnivariateSpline
+from scipy.linalg import cho_factor, cho_solve
+from numpy.linalg import slogdet
+from astropy.stats import sigma_clip
+from astropy.analytic_functions import blackbody_lambda
+from astropy import units as u
+
+import gc
+import logging
+
+from itertools import chain
+#from collections import deque
+from operator import itemgetter
+import yaml
+import shutil
+import json
+
+from star_base import Order as OrderBase
+from star_base import SampleThetaPhi as SampleThetaPhiBase 
+from model_BB_varA_K import ThetaParamDelR as ThetaParam
+from model_BB_varA_K import PhiParam
+
+from sklearn.mixture import GMM
+
+Starfish.routdir = ""
+
+# list of keys from 0 to (norders - 1)
+order_keys = np.arange(1)
+DataSpectra = [DataSpectrum.open(os.path.expandvars(file), orders=Starfish.data["orders"]) for file in Starfish.data["files"]]
+# list of keys from 0 to (nspectra - 1) Used for indexing purposes.
[…]

### 2017-05-15 sf/exp10/output/bb_absolute/run02/user_prior.py
Starfish config files for experiment 10, runs 1 and 2

@@ -1,0 +1,26 @@
+def user_defined_lnprior(p):
+    '''
+    Takes a vector of stellar parameters and returns the ln prior.
+    '''
+    if not ( (p[2] < 0.5) and (p[2] > 0) and
+             (p[3] < 1000.0) and (p[3] > -1000.0) and
+             (p[4] < 10000.0) and (p[4] > 0.01) and
+             (p[6] < 1500.0) and (p[6] > 1000.0) and
+             (p[8] < 20.0) and (p[8] > 0.0) and
+             (p[9] < -1.7) and (p[9] > -2) and
+             (p[13] > 0.0) and (p[13] < 2.0) and
+             (p[14] < -1.0) and (p[14] > -3.0) and
+             (p[15] > 0.0) and (p[15] < 300 ) ):
+
+    	return -np.inf
+    
+    # Solar metalicity to within +/- 0.05 dex
+    lnp_FeH = -1.0*(p[2] - 0.01)**2/(2.0*0.001**2)
+    lnp_vz = -1.0*(p[3] - 110.0)**2/(2.0*20.0**2)
+    lnp_l = -1.0*(p[15] - 124.4)**2/(2.0*10.0**2)
+    lnp_logAmp = -1.0*(p[14] + 1.40)**2/(2.0*0.03**2)
+    # No prior on v_z.
+    ln_prior_out = lnp_FeH + lnp_vz + lnp_l + lnp_logAmp
+
+    return ln_prior_out
+

### 2017-05-22 code/star_proto_varA_K_delV.py
Code with revised spectral resolution treatment

@@ -95,20 +95,15 @@ class Order(OrderBase):
         # the grid spacing. Therefore skip the convolution step if we have
         # values smaller than this.
         # FFT and convolve operations
-        if p.delR < 0.0:
-            raise C.ModelError("delR must be positive")
-        elif p.delR < 0.01:
-            # Skip the delR taper due to instrumental effects
-            eigenspectra_full = self.EIGENSPECTRA.copy()
-        else:
-            FF = np.fft.rfft(self.EIGENSPECTRA, axis=1)
+        FF = np.fft.rfft(self.EIGENSPECTRA, axis=1)
 
-            sigma = 299792.46/p.delR / 2.35 # in km/s
-            taper = np.exp(-2 * (np.pi ** 2) * (sigma ** 2) * (self.ss ** 2))
-            FF_tap = FF * taper
+        #delR is now rebranded as deltaV, the FWHM of velocity resolution
+        sigma = p.delR / 2.35 # in km/s
+        taper = np.exp(-2 * (np.pi ** 2) * np.sign(sigma)*(sigma ** 2) * (self.ss ** 2))
+        FF_tap = FF * taper
 
-            # do ifft
-            eigenspectra_full = np.fft.irfft(FF_tap, self.pca.npix, axis=1)
+        # do ifft
+        eigenspectra_full = np.fft.irfft(FF_tap, self.pca.npix, axis=1)
 
         # Spectrum resample operations
         if min(self.wl) < min(wl_FFT) or max(self.wl) > max(wl_FFT):

### 2017-05-22 document/ms.tex
Add lots of text and some edits to the manuscript

@@
 \section{Introduction}\label{sec:intro}
-The method is from \citep{czekala15}.  It is similar to \citep{2017ApJ...836..200G}.
 
-\subsection{Protostars}
-\subsection{Previous studies of protostar photospheres}
-\subsection{Previous studies of S68N}
+\textbf{todo: T.P.G text}
 
@@
 The \texttt{NIRSPEC-7} filter provided 1.84$-$2.63 $\mu$m wavelength range, with native spectral resolution of $R=1250$ from a 0\farcs76 (4 pixels) $\times$ 42\farcs0 slit.
-The individual epochs were coadded to form a single composite spectrum of signal to noise ratio $S/N\sim30$.
+The individual epochs were coadded to form a single composite spectrum of signal to noise ratio $S/N\sim30$ per pixel.
+
+The reduced spectrum contained H$_2$ lines indicative of excited gas emission.These lines were fitted and removed from the spectrum to produce a composite sprectrum assumed to possess only stellar photosphere and circumstellar disk emission.
 
@@
 
-Our approach involves Bayesian forward modeling of the observed spectrum under a range of different assumptions about the protostellar system.
+Our analysis approach involves Bayesian forward modeling of the observed spectrum under a range of different assumptions about the protostellar system.
 We discuss the limitations of our assumptions in the discussion section.
@@
 We assume that stellar photosphere and warm circumstellar disk emission dominate the radiation in the near-IR $K-$band.
-We constructed a forward model for the observed Keck spectrum using the spectral inference framework \texttt{Starfish} from \citet{czekala15} with support for mixture model modifications from \citet{2017ApJ...836..200G}.
+We constructed a forward model for the observed Keck spectrum using the spectral inference framework \texttt{Starfish} from \citet{czekala15} with support for mixture model modifications similar to \citet{2017ApJ...836..200G}.
 The mixture model for S68N's Keck spectrum is:
@@
 \begin{eqnarray} \label{eqn:mix_M}
-	S_{\mathrm{mix}} = \Omega_{\mathrm{\star}} B(\teffa)  + \Omega_{\mathrm{d}} B(\teffb)
+	S_{\lambda, \mathrm{mix}} = \Omega_{\mathrm{\star}} I_{\lambda}(\teffa)  + \Omega_{\mathrm{d}} B_{\lambda}(\teffb)
 \end{eqnarray}
-where $B(T)$ is the spectral radiance as a function of temperature.  The ratio of solid angles relates the relative size of the emission regions:
+where $I_{\lambda}(\teffa)$ and $B_{\lambda}(T)$ are spectral irradiances as a function of temperature for the star and disk respectively.
+Assuming the star and disk emission originate at the same distance $d$, the ratio of solid angles relates the projected area of the emission regions.
 \begin{eqnarray} \label{eqn:fill_factor}
-	\frac{\Omega_d}{\Omega_\star} = \frac{r_d^2 d^2}{r_\star^2 d^2} = \frac{r_d^2}{r_\star^2}
+	\frac{\Omega_d}{\Omega_\star} = \frac{A_d d^2}{A_\star d^2} = \frac{A_d}{A_\star}
 \end{eqnarray}
 
-approximating the circumstellar disk emission as a face-on circle.
-More accurate estimates for the disk emission and geometries could be obtained from rigorous radiative transfer methods \citep[\emph{e.g.}]{2017arXiv170305765R}.
-We model the protostellar spectral radiance $B(T_\star)$ with \PHOENIX\ synthetic model spectra possessing an unknown-but-low surface gravity $\logg \in [2.0,4.0]$ in cm$/$s$^2$ and an effective temperature $\teffa \in [2700,3600]$ K.
-The circumstellar disk radiance is assumed to be black body, with a temperature range $\teffb \in [1000,1700]$ K capped by the temperature at which typical dust sublimates.
+We model the protostellar spectral radiance $I_{\lambda}(T_\star)$ with \PHOENIX\ synthetic model spectra \citep{husser13} possessing an unknown-but-low surface gravity $\logg \in [2.0,4.0]$ in cm$/$s$^2$ and an effective temperature $\teffa \in [2700,3600]$ K.
+The circumstellar disk irradiance is assumed to be black body, with a temperature range $\teffb \in [1000,1500]$ K capped by the temperature at which typical dust sublimates.
 
 The radiated spectrum passes through an unknown amount of extinction and scattering, altering its spectral shape in an uncertain---and potentially irretrievable---way.
-We explored several options for characterizing the extinction towards S68N.
-First, instead of characterizing the spectral slope by a reddening law and extinction, $A_V$, we instead assumed that the overall spectral shape is approximated by a third order polynomial \footnote{The polynomial is parameterized as a linear combination of Chebyshev polynomials truncated to the first 3 non-constant terms.}.
-The polynomial coefficients lacked interpretability, and may not have adequately approximated extinction power laws, so we also experimented with an $A_K$ and a power law slope:
+We characterize the reddening with an $A_K$ and a power law slope:
 
@@
 
-with $\alpha \in [-2, -1.7]$ representing the power law exponent that may depend on dust properties and degree of extinction.  The extinction is then defined as:
+with $\alpha \in [1.7, 2]$ representing the power law exponent that may depend on dust properties and degree of extinction \textbf{cite}.
 
-$$ 10^{-0.4 A_\lambda}$$
+The wavelength-domain follows a similar scaling to \citet{czekala15}, with slight modification.
+Here we remove the $\vsini$ broadening kernel, since the $R\sim1250$ spectral resolution is too low to provide a meaningful constraint on projected stellar rotation.
+Instead, we replace $\vsini$ with a nuisance parameter to characterize the uncertainty in effective instrumental spectral resolution broadening kernel $\mathcal{F}_v^{\rm inst}$, parameterized as small perturbations from our estimated instrumental resolution $R_{\mathrm{net}} = (1250^{-2} + \delta R^{-2} )^{-1/2}$.
+The instrumental-broadened mixture model is then:
+
+\begin{equation} \label{eqn:broadening}
+S_{\lambda, \mathrm{mix}}(\vt_{\ast}, \sigma_v, v_r) = \flam(\vt_{\ast}) \ast \mathcal{F}_v^{\rm inst} \ast \mathcal{F}_v^{\rm dop}
+\end{equation}
+
+The Dopler shift is similarly treated as a nuisance parameter, but is nonetheless included in the model to provide robustness in the face of imperfect instrumental calibration.
+Extinction and re-sampling proceed identically to \citet{czekala15}.
 
@@
 We see H$_2$ emission lines in the $K-$band spectrum of S68N, so some degree of accretion is likely ongoing, potentially contributing non-negligible veiling in the photospheric absorption lines.
-In any case, the limited spectral information available does not permit a more detailed treatment of accretion or disk gas emission as is possible with higher spectral resolution \citep[\emph{e.g.}]{2016ApJ...826..179L}.
+In any case, the limited spectral information available does not permit a more detailed treatment of accretion or disk gas emission as is possible with higher spectral resolution \citep[][\emph{e.g.}]{2016ApJ...826..179L}.
+
+\subsection{MCMC details}
+
+We used MCMC ensemble sampling to deliver a joint posterior probability distribution function for the astrophysical, instrumental, and nuissance parameters.
+The method employed `emcee` \citep{foreman13} to provide resilience against sampling strongly degenerate parameters such as solid angles and temperatures of the mixture model.
+We ran the MCMC sampler with 5000 steps and 40 walkers, selecting the final $\sim200-1000$ steps as adequately devoid of hysteresis from initial conditions.
+
+\section{Results}
+
+\subsection{Low inferred surface gravity and comparison to evolutionary models}
+
+We find a surface gravity in the range of $\logg = 2.x-3.x$, marginalizing over all other (uncertain) stellar, disk, and nuissance parameters.
+This low alebit uncertain surface gravity firmly places the object in the realm of low mass protostars-- still undergoing gravitational contraction and accretion, and therefore possessing a relatively large radius with only a faction of its fated stellar mass.
+Figure \ref{fig:theory_v_obs} shows a two panel plot of the joint posterior on stellar surface gravity and effective temperature.
+Theoretical pre-main sequence stellar evolutionary model tracks computed for ages $>1$ Myr \texttt{baraffe15} occupy regions with $2800 < \teff (\mathrm{K}) < 4000$ and $3.3<\logg$.
+Surface gravities lower than this 3.3 threshold should presumably be less evolved and younger protostars.
+Observations roughly agree.
+For example, the $\sim 2$ Myr IC348 occupies a space around $3.3 < \logg <4.2$, while the $\sim 120 Myr$ Pleiades resides around $\logg\sim 4.5$, with warmer average temperatures.
+Class I protostars \citep{2005AJ....130.1145D} occupy a broad range of measured and constrained effective temperatures and surface gravities, with relatively large uncertainties owing to the difficulty of simultaneously assigning surface gravity in the face of uncertain veiling measurements.
+
+The joint, marginalized, posterior probability distribution for S68N is shown in the right panel of Figure \ref{fig:theory_v_obs}.
+The majority of probability density is below all previous measurements.
+
+\subsection{Reasonable Effective Temperature}
+%TODO, maybe move to above section
+
+\begin{figure*}[b]
+ \centering
+ \includegraphics[width=0.85\textwidth]{figures/Class0_Teff_logg_2panel.pdf}
+ \caption{Pre-main sequence and protostar evolution comparison between theory (left panel) and obseration (right panel).
+The 0.02$-$1.2 $M_{\odot}$ evolutionary model tracks are from \citet{baraffe15}, spanning 1 Myr to 100 Myr isochrones; protostars are expected to sit below the 1 Myr isochrone in the region of parameter space demarcated with a yellow dashed ellipse.
+The observations show coarse agreement with the models-- measurements of the Pleiades from \citet[green KDE]{cottaar14} cluster around the 100 Myr isochrone, although extend into higher-than-predicted $\log{g}$ for hotter stars.
+The younger IC348 sources \citep[purple KDE]{cottaar14} cluster with a large spread above and below the $\sim10$ Myr isochrone.
+The source S 68N has a broad posterior PDF placing its maximum a-posteriori estimate inside the range of protostars.
+The black dots are Class I protostars from \citet{2005AJ....130.1145D}, showing a large range in measured properties with relatively large uncertainties in $\log{g}$.}
+ \label{fig:theory_v_obs}
+\end{figure*}
+
+\subsection{Constraints on disk/envelope emission}
+
+The observed S68N spectrum supports non-zero veiling from an extra smooth emission component, presumably either a circumstellar disk or envelope reradiating reprocessed starlight.
+The simplistic black body model allows the construction of the relative emitting areas of disk to star.
+from the solid
+
+\subsection{High extinction}
+
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.85\textwidth]{figures/S68N_spectrum.pdf}
+ \caption{Observed and modeled spectrum of S68N with residual noise spectrum.}
+ \label{fig:S68N_spectrum}
+\end{figure*}
+
+Here is another new figure:
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.85\textwidth]{figures/r_K_vs_Omega.pdf}
+ \caption{The projected joint distribution of $\hat r_K$ with disk to star solid angle ratio and characteristic disk temperature.}
+ \label{fig:omega_rat}
+\end{figure*}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.45\textwidth]{../plots/logg_omega_phys.pdf}
+ \caption{Posterior probability distribution function from Experiment 3, Run1, marginalized over all stellar and nuisance parameters except $\logg$ and $\Omega_d/\Omega_\star$.
+The surface gravity correlates with the solid angle ratio since both of these factors affect the CO line depths.
+Lines of differing stellar mass and disk radii are shown for a range of stellar radii.}
+ \label{fig:posterior_loggOmega}
+\end{figure}
+
+~\clearpage
+
+\section{Discussion}
+
+Our spectral inference methodology made some necessary simplifying assumptions in order to assess the relative strengths of the components giving rise to the observed, composite Keck NIRSPEC spectrum of S68N.
+Below we list the assumptions in order of how \emph{strong} they are, and gauge their impact on our results.
+
+\begin{enumerate}
+\item There is no other emission source, other than photosphere and black body disk.  Particularly, line emission veiling and accretion continuum veiling are ignored.
+\item Phoenix models approximate emission of protostellar photospheres.
+\item The photospheric temperature is in the range $\teffa \in [2700,3600]$ K.
+\item The disk radiates as a single component black body in the range $\teffb \in [1000,1500]$ K.
+\item The disk and stellar photosphere undergo the same extinction wavelength dependence and extent.
+\item A single correlation scale length and amplitude characterizes the noise model mismatch between model and data.
+\item Metallicity departs negligibly from Solar.
+\end{enumerate}
+
+We know other emission sources, beyond quiescent photosphere and disk.
+The raw spectrum of S68N shows H$_2$ emission lines indicative of either shocked material or accretion.
+Higher spectral resolution observations of protostars have shown CO emission \texttt{cite- seokho lee, etc.}.
+With our NIRSPEC observations alone, it is impossible to assess whether CO emission partially fills in the CO lines at $2.3-2.4 \;\mu$m.
+Such line veiling would tend to reduce the equivalent widths of the CO lines, and bias our accretion-free estimate towards either \emph{higher} surface gravity or \emph{higher} veiling.
+In other words, the ``true'' surface gravity and veiling is lower than our posterior would suggest.
+We already derive a very low surface gravity, so it would be hard to imagine an even lower number, reinforcing our assumption in the first place.
+
+Our model employs spectrally emulated Phoenix models to simulate the photospheric emission of S68N.
+Template photospheres of Class 0 protostars are not yet available due to the prohibitive difficulty of observations with existing facilities and high veiling.
+Protostellar photospheric emission could depart from Phoenix models based on non-standard physics not currently included in the stellar atmospheric modelling.
+For example strong magnetic fields, starspots, and other factors would alter the photospheric emergent spectrum's appearance from what we have assumed here.
+These non-standard physical phenomena would largely impact relatively weak features of the spectral mostly perceptible at higher spectral resolution.
+A large coverage fraction of cool starspots could distort our derived protostellar solid angle towards lower values and higher effective temperatures than reality.
+The physical effects of starspots on more evolved Class II and Class III stars are still actively being studied \texttt{cite gully-santiago, fang, etc.}, so it is not clear how Class 0 protostars compare.
+
+We have assumed the disk radiates as a black body of a single temperature.
+More accurate estimates for the disk emission and geometries could be obtained from rigorous radiative transfer methods \citep[\emph{e.g.}]{2017arXiv170305765R}; no such advanced disk modeling was attempted.
+The relatively narrow $K-$ observation band does not offer a large enough lever arm to distinguish the nearly degenerate effects of elevated disk temperature versus increased solid angle of emission.
+It is unlikely that our limited spectral-grasp data would be able to place informative constraints on even more disk properties, nor would those revised models improve our fit quality significantly.
+Although the black body model was a simplifying assumption, it has produced a reasonable solid angle ratio posterior distribution.
+
+We have assumed the disk and protostar undergo the same extent and wavelength-dependence of extinction.
+In principle, the starlight pass through a flared circumestellar disk or envelope, while the disk emission passess through relatively less (or more) material, causing differential extinction between disk and star.
+The relatively small solid angle ratio of the disk suggests that if the disk emitting material is distributed in an azimuthally symmetric ring around the star, the disk should be quite close to the protostellar surface, reinforcing our assumption that the emission sources pass through the same material.
+
+%TODO-- check the equilibrium distance for a dust grain to emit at a temperature T_d and receive flux of temperature T_eff-- does it agree with the solid angle ratio?
+
+\subsection{Simulated JWST Observations of S68N}
+
+Below is a simulated spectrum of S68N with the JWST NIRSPEC IFU with the G235M grating providing $R\sim1000$ across $1.7-3.0 \; \mu$m, with a $S/N \sim 100$ per pixel.
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.45\textwidth]{figures/simulated_JWST_S68N.pdf}
+ \caption{Simulated JWST observation of S68N.}
+ \label{fig:JWST}
+\end{figure}
+
+\clearpage
+\pagebreak
+
+\appendix
+
+\section{Adaptations of Starfish to handle absolute flux and solid angle}
+The original \texttt{Starfish} framework flux-standardized its emulated spectra to remove uninteresting correlations in effective temperature and solid angle.
+Here we return the mean flux levels to provide an accurate estimate of $\Omega$.
 
@@
 
-\section{Results}
-
-\subsection{Experiment 3, Run 1}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.45\textwidth]{../plots/logg_omega_phys.pdf}
- \caption{Posterior probability distribution function from Experiment 3, Run1, marginalized over all stellar and nuisance parameters except $\logg$ and $\Omega_d/\Omega_\star$.
-The surface gravity correlates with the solid angle ratio since both of these factors affect the CO line depths.
-Lines of differing stellar mass and disk radii are shown for a range of stellar radii.}
- \label{fig:posterior_loggOmega}
-\end{figure}
-
-~\clearpage
-
-\begin{figure*}[b]
- \centering
- \includegraphics[width=0.85\textwidth]{../plots/gully_Class0_Teff_logg_results.pdf}
- \caption{Pre-main sequence and protostar evolution comparison between theory (left panel) and obseration (right panel).
-The 0.02$-$1.2 $M_{\odot}$ evolutionary model tracks are from \citet{baraffe15}, spanning 1 Myr to 100 Myr isochrones; protostars are expected to sit below the 1 Myr isochrone in the region of parameter space demarcated with a yellow dashed ellipse.
-The observations show coarse agreement with the models-- measurements of the Pleiades from \citet[green KDE]{cottaar14} cluster around the 100 Myr isochrone, although extend into higher-than-predicted $\log{g}$ for hotter stars.
-The younger IC348 sources \citep[purple KDE]{cottaar14} cluster with a large spread above and below the $\sim10$ Myr isochrone.
-The source S 68N has a broad posterior PDF (Experiment 4-teal KDE, Experiment 3- red/brown KDE) placing its maximum a-posteriori estimate inside the range of protostars, regardless of experimental assumptions.
-The black dots are Class I protostars from \citet{2005AJ....130.1145D}, showing a large range in measured properties with relatively large uncertainties in $\log{g}$.}
- \label{fig:theory_v_obs}
-\end{figure*}
-
-\section{Discussion}
-
-\clearpage
-\pagebreak
-
-\appendix
-
-\section{Adaptations of Starfish to handle absolute flux and solid angle}
-
 \acknowledgements

### 2017-05-22 sf/exp12/output/bb_absolute/run02/user_prior.py
Starfish configuration files for experiments 10 and 12

@@ -1,0 +1,26 @@
+def user_defined_lnprior(p):
+    '''
+    Takes a vector of stellar parameters and returns the ln prior.
+    '''
+    if not ( (p[2] < 0.5) and (p[2] > 0) and
+             (p[3] < 1000.0) and (p[3] > -1000.0) and
+             (p[4] < 30) and (p[4] > -30) and
+             (p[6] < 1500.0) and (p[6] > 1000.0) and
+             (p[8] < 20.0) and (p[8] > 0.0) and
+             (p[9] < -1.7) and (p[9] > -2) and
+             (p[13] > 0.0) and (p[13] < 2.0) and
+             (p[14] < -1.0) and (p[14] > -3.0) and
+             (p[15] > 0.0) and (p[15] < 300 ) ):
+
+    	return -np.inf
+    
+    # Solar metalicity to within +/- 0.05 dex
+    lnp_FeH = -1.0*(p[2] - 0.01)**2/(2.0*0.001**2)
+    lnp_vz = -1.0*(p[3] - 110.0)**2/(2.0*20.0**2)
+    lnp_l = -1.0*(p[15] - 124.4)**2/(2.0*10.0**2)
+    lnp_logAmp = -1.0*(p[14] + 1.40)**2/(2.0*0.03**2)
+    # No prior on v_z.
+    ln_prior_out = lnp_FeH + lnp_vz + lnp_l + lnp_logAmp
+
+    return ln_prior_out
+

### 2017-05-23 document/ms.tex
Update the text and figures after reviewing and hand-editing printed document

@@
 
-\author{T.B. Determined,\altaffilmark{1}}
-
-\altaffiltext{1}{NASA Ames}
+\author{Thomas P. Greene, Michael A. Gully-Santiago}
+\affil{NASA Ames Research Center, Space Science and Astrobiology Division, 
+M.S. 245-6; Moffett Field, CA 94035}
+\author{M. Barsony}
+\affil{SETI}
 
@@
 
-\textbf{todo: T.P.G text}
+\textbf{todo: T.P.G introductory text}
 
@@
 The observations of S68N were carried out with NIRSPEC on the Keck telescope over 5 epochs from 2003-2014.
-The \texttt{NIRSPEC-7} filter provided 1.84$-$2.63 $\mu$m wavelength range, with native spectral resolution of $R=1250$ from a 0\farcs76 (4 pixels) $\times$ 42\farcs0 slit.
+The \texttt{NIRSPEC-7} filter provided 1.84$-$2.63 $\mu$m wavelength range, with native spectral resolution of $R \equiv \frac{\lambda}{\delta \lambda} =1250$ from a 0\farcs76 (4 pixels) $\times$ 42\farcs0 slit.
 The individual epochs were coadded to form a single composite spectrum of signal to noise ratio $S/N\sim30$ per pixel.
@@
 The reduced spectrum contained H$_2$ lines indicative of excited gas emission.These lines were fitted and removed from the spectrum to produce a composite sprectrum assumed to possess only stellar photosphere and circumstellar disk emission.
+
+\textbf{todo: T.P.G data reduction text:}
+\begin{enumerate}
+	\item Night sky lines as possible correlated residual structure
+	\item etc.
+\end{enumerate}
 
@@
 We assume that stellar photosphere and warm circumstellar disk emission dominate the radiation in the near-IR $K-$band.
-We constructed a forward model for the observed Keck spectrum using the spectral inference framework \texttt{Starfish} from \citet{czekala15} with support for mixture model modifications similar to \citet{2017ApJ...836..200G}.
+We constructed a forward model for the observed Keck spectrum using the spectral inference framework \texttt{Starfish} from \citet[hereafter \texttt{C15}]{czekala15} with support for mixture model modifications similar to \citet{2017ApJ...836..200G}.
 The mixture model for S68N's Keck spectrum is:
@@
 \begin{eqnarray} \label{eqn:mix_M}
-	S_{\lambda, \mathrm{mix}} = \Omega_{\mathrm{\star}} I_{\lambda}(\teffa)  + \Omega_{\mathrm{d}} B_{\lambda}(\teffb)
+	S_{\lambda, \mathrm{mix}} = \Omega_{\mathrm{\star}} I_{\lambda}(\vt_{\ast})  + \Omega_{\mathrm{d}} B_{\lambda}(\teffb)
 \end{eqnarray}
-where $I_{\lambda}(\teffa)$ and $B_{\lambda}(T)$ are spectral irradiances as a function of temperature for the star and disk respectively.
+where $\vt_{\ast} = (\teff, \logg, \Z)$ are the protostellar photospheric parameters, and $I_{\lambda}$ and $B_{\lambda}$ are spectral irradiances for the star and disk respectively.
 Assuming the star and disk emission originate at the same distance $d$, the ratio of solid angles relates the projected area of the emission regions.
@@
 We model the protostellar spectral radiance $I_{\lambda}(T_\star)$ with \PHOENIX\ synthetic model spectra \citep{husser13} possessing an unknown-but-low surface gravity $\logg \in [2.0,4.0]$ in cm$/$s$^2$ and an effective temperature $\teffa \in [2700,3600]$ K.
+We assume metallicity is negligibly close to solar.
 The circumstellar disk irradiance is assumed to be black body, with a temperature range $\teffb \in [1000,1500]$ K capped by the temperature at which typical dust sublimates.
@@
 The radiated spectrum passes through an unknown amount of extinction and scattering, altering its spectral shape in an uncertain---and potentially irretrievable---way.
-We characterize the reddening with an $A_K$ and a power law slope:
+Nevertheless, we characterize the reddening with an $A_K$ and a power law slope:
 
@@
 
-with $\alpha \in [1.7, 2]$ representing the power law exponent that may depend on dust properties and degree of extinction \textbf{cite}.
+with $\alpha \in [1.7, 2]$ representing the power law exponent that may depend on dust properties and degree of extinction \citep{2005MNRAS.359..589M}.
 
@@
 Here we remove the $\vsini$ broadening kernel, since the $R\sim1250$ spectral resolution is too low to provide a meaningful constraint on projected stellar rotation.
-Instead, we replace $\vsini$ with a nuisance parameter to characterize the uncertainty in effective instrumental spectral resolution broadening kernel $\mathcal{F}_v^{\rm inst}$, parameterized as small perturbations from our estimated instrumental resolution $R_{\mathrm{net}} = (1250^{-2} + \delta R^{-2} )^{-1/2}$.
+Instead, we replace $\vsini$ with a nuisance parameter to characterize the uncertainty in effective instrumental spectral resolution broadening kernel $\mathcal{F}_v^{\rm inst}$, parameterized as small perturbations from our estimated instrumental resolution $\delta v_{\mathrm{eff}}^2 = (240 \; \mathrm{km \;s}^{-1})^2 \pm \epsilon^2$.
 The instrumental-broadened mixture model is then:
@@
 \begin{equation} \label{eqn:broadening}
-S_{\lambda, \mathrm{mix}}(\vt_{\ast}, \sigma_v, v_r) = \flam(\vt_{\ast}) \ast \mathcal{F}_v^{\rm inst} \ast \mathcal{F}_v^{\rm dop}
+S(\vt_{\ast}, \delta v, v_r) = S_{\lambda, \mathrm{mix}} \ast \mathcal{F}_v^{\rm inst} \ast \mathcal{F}_v^{\rm dop}
 \end{equation}
 
-The Dopler shift is similarly treated as a nuisance parameter, but is nonetheless included in the model to provide robustness in the face of imperfect instrumental calibration.
-Extinction and re-sampling proceed identically to \citet{czekala15}.
+The Doppler shift is similarly treated as a nuisance parameter, but is nonetheless included in the model to provide robustness in the face of imperfect instrumental calibration.
+We also apply a third order Chebyshev polynomial with parameters $c^i$, and the same flexible covariance matrix $\vC$ as in \texttt{C15}.
+Extinction and re-sampling proceed identically to \texttt{C15} to produce a pixel-level forward model $\vM$, containing 16 parameters.
 
@@
 This assumption almost certainly fails for Class 0 protostars, which are still actively accreting a large fraction of their mass.
-We see H$_2$ emission lines in the $K-$band spectrum of S68N, so some degree of accretion is likely ongoing, potentially contributing non-negligible veiling in the photospheric absorption lines.
-In any case, the limited spectral information available does not permit a more detailed treatment of accretion or disk gas emission as is possible with higher spectral resolution \citep[][\emph{e.g.}]{2016ApJ...826..179L}.
+See \S \ref{sec:discussion} for discussion of the limitations of the model assumptions.
 
@@
 We used MCMC ensemble sampling to deliver a joint posterior probability distribution function for the astrophysical, instrumental, and nuissance parameters.
-The method employed `emcee` \citep{foreman13} to provide resilience against sampling strongly degenerate parameters such as solid angles and temperatures of the mixture model.
+The method employs \texttt{emcee} \citep{foreman13} to provide resilience against sampling strongly degenerate parameters such as solid angles and temperatures of the mixture model.
 We ran the MCMC sampler with 5000 steps and 40 walkers, selecting the final $\sim200-1000$ steps as adequately devoid of hysteresis from initial conditions.
@@
 
+\subsection{Reasonable Effective Temperature}
+The \citet{baraffe15} model tracks do not extend to ages $<1 $ Myr, but we expect the range of effective temperatures at such young ages to be comparable to the projections at 1 Myr based on extensions to the Hayashi track.
+If so, the range of temperatures derived for S68N place it in the expected range of protostars.
+Notably, we only searched for effective temperatures in the range $\teff \in [2700,3600] \; \mathrm{K}$, so our method was unable to probe higher or lower possible temperatures.
+However our posterior samples do not ``pile-up'' near the parameter ranges as one would observe in an overly-restrictive parameter range.
+Instead our smooth posterior places most of its support in the middle of the effective temperature range.
+
 \subsection{Low inferred surface gravity and comparison to evolutionary models}
@@
 We find a surface gravity in the range of $\logg = 2.x-3.x$, marginalizing over all other (uncertain) stellar, disk, and nuissance parameters.
-This low alebit uncertain surface gravity firmly places the object in the realm of low mass protostars-- still undergoing gravitational contraction and accretion, and therefore possessing a relatively large radius with only a faction of its fated stellar mass.
+This low alebit uncertain surface gravity places the object in the realm of low mass protostars-- still undergoing gravitational contraction and accretion, and therefore possessing a relatively large radius with only a faction of its fated stellar mass.
 Figure \ref{fig:theory_v_obs} shows a two panel plot of the joint posterior on stellar surface gravity and effective temperature.
-Theoretical pre-main sequence stellar evolutionary model tracks computed for ages $>1$ Myr \texttt{baraffe15} occupy regions with $2800 < \teff (\mathrm{K}) < 4000$ and $3.3<\logg$.
+Theoretical pre-main sequence stellar evolutionary model tracks computed for ages $>1$ Myr \citep{baraffe15} occupy regions with $2800 < \teff (\mathrm{K}) < 4000$ and $3.3<\logg$.
 Surface gravities lower than this 3.3 threshold should presumably be less evolved and younger protostars.
@@
 
-\subsection{Reasonable Effective Temperature}
-%TODO, maybe move to above section
-
-\begin{figure*}[b]
+\begin{figure}
  \centering
- \includegraphics[width=0.85\textwidth]{figures/Class0_Teff_logg_2panel.pdf}
+ \includegraphics[width=1.0\columnwidth]{figures/Class0_Teff_logg_2panel.pdf}
  \caption{Pre-main sequence and protostar evolution comparison between theory (left panel) and obseration (right panel).
-The 0.02$-$1.2 $M_{\odot}$ evolutionary model tracks are from \citet{baraffe15}, spanning 1 Myr to 100 Myr isochrones; protostars are expected to sit below the 1 Myr isochrone in the region of parameter space demarcated with a yellow dashed ellipse.
+The 0.02$-$1.2 $M_{\odot}$ evolutionary model tracks are from \citet{baraffe15}, spanning 1 Myr to 1 Gyr isochrones; protostars are expected to sit below the 1 Myr isochrone in the region of parameter space demarcated with a yellow dashed ellipse.
 The observations show coarse agreement with the models-- measurements of the Pleiades from \citet[green KDE]{cottaar14} cluster around the 100 Myr isochrone, although extend into higher-than-predicted $\log{g}$ for hotter stars.
@@
  \label{fig:theory_v_obs}
-\end{figure*}
+\end{figure}
 
@@
 
-The observed S68N spectrum supports non-zero veiling from an extra smooth emission component, presumably either a circumstellar disk or envelope reradiating reprocessed starlight.
-The simplistic black body model allows the construction of the relative emitting areas of disk to star.
-from the solid
+The observed S68N spectrum is consistent with modest veiling from an extra smooth emission component, presumably either a circumstellar disk or envelope reradiating reprocessed starlight.
+The traditional observational metric for assessing veiling is the so-called $r_\lambda$-factor, the ratio of disk to photospheric flux, with the photospheric flux usually defined as the continuum.
+The right thing to do would be to compute the veiling by integrating the ratios of our forward modeled disk and photosphere spectrum over a relevant filter curve:
 
-\subsection{High extinction}
+\begin{eqnarray}
+r_{K} &=& \int_{K} \frac{f_{d}}{f_{\star}} t(\lambda) d\lambda
+\end{eqnarray}
 
-\begin{figure*}
- \centering
- \includegraphics[width=0.85\textwidth]{figures/S68N_spectrum.pdf}
- \caption{Observed and modeled spectrum of S68N with residual noise spectrum.}
- \label{fig:S68N_spectrum}
-\end{figure*}
+where $t(\lambda)$ is the normalized wavelength-dependent transmission of the filter.
+In practice our observation band does not extend to the ends of $K-$band, so the accuracy of such an estimate would be limited to our projected flux ratio outside the observation window.
+So instead, we simply report the median pixel of the $r_\lambda$ vector in our band $\hat r_K = r_\lambda |_{50\%}$, which coarsely approximates $r_K$.
+In practice, the distribution of $\hat r_K$ is much larger than the uncertainty attributable to this approximation.
+We find a distribution of $\hat r_K \in [0, 0.4]$, with a peak near 0.
 
-Here is another new figure:
-\begin{figure*}
- \centering
- \includegraphics[width=0.85\textwidth]{figures/r_K_vs_Omega.pdf}
- \caption{The projected joint distribution of $\hat r_K$ with disk to star solid angle ratio and characteristic disk temperature.}
- \label{fig:omega_rat}
-\end{figure*}
+The simplistic black body model allows the construction of the relative emitting areas of disk to star as defined in Equation \ref{eqn:fill_factor}.
+The relative areas are strongly dependent upon the assumptions of the effective temperatures of the star and disk.
+Figure \ref{fig:omega_rat} demonstrates one projection of the degenerate hyperspace relating disk temperature, solid angle ratio, and $\hat r_K$.
+Disk temperatures of $T_d \sim 1500\;(\mathrm{K})$ result in emitting areas of the disk comparable to the projected area of the stellar photosphere, and providing much less disk flux than photosphere flux.
 
@@
  \centering
- \includegraphics[width=0.45\textwidth]{../plots/logg_omega_phys.pdf}
+ \includegraphics[width=0.85\columnwidth]{figures/r_K_vs_Omega.pdf}
+ \caption{The projected joint distribution of $\hat r_K$ with disk to star solid angle ratio and characteristic disk temperature.}
+ \label{fig:omega_rat}
+\end{figure}
+
+\subsection{High extinction}
+The Keck NIRSPEC spectrum of S68N shows a spectral flux density increasing with wavelength.
+The Phoenix photopheric model predicts a spectral flux density decreasing with wavelength for the range of best fit photospheric temperatures.
+The red slope indicates a high degree of reddening.
+Our posterior constraints confirm large values of extinction indicative of either a highly embedded source or a background object.
+Figure \ref{fig:A_K_plot} shows the joint constraint on $A_K$ and $\alpha$, the power law extinction slope.
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.85\columnwidth]{figures/AK_alpha.pdf}
+ \caption{Extinction and power law slope distributions, with effective temperature dependence.}
+ \label{fig:A_K_plot}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.85\columnwidth]{figures/S68N_spectrum.pdf}
+ \caption{Observed and modeled spectrum of S68N with residual noise spectrum.}
+ \label{fig:S68N_spectrum}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.85\columnwidth]{../plots/logg_omega_phys.pdf}
  \caption{Posterior probability distribution function from Experiment 3, Run1, marginalized over all stellar and nuisance parameters except $\logg$ and $\Omega_d/\Omega_\star$.
@@
 
+%Table
 ~\clearpage
 
-\section{Discussion}
+\begin{tabular}{lp{3cm}rrr}
+\hline
+\multicolumn{4}{c}{Marginal PDF} \\
+\cline{3-5}
+Parameter & Description & $|_{16\%}$& Median & $|_{84\%}$ \\
+\hline
+$\teff$   & Stellar effective temperature  (K) &   3000 & 3200 & 3600  \\
+$\logg$   & Surface gravity & 2 & 3 & 4 \\
+$\Z$   & Metallicity & - & - & - \\
+$v_r$   & Velocity error & - & - & - \\
+$\epsilon$   & Resolution error & - & - & - \\
+$\Omega_\star/\Omega_d$   & Star/Disk solid angle ratio  & - & - & - \\
+$\hat r_K$   & Estimated $K-$band veiling  & - & - & - \\
+$T_d$   & Black body disk temperature & - & - & - \\
+$A_K$   & $K-$band extinction & - & - & - \\
+$\alpha$   & Exponent of reddening law & - & - & - \\
+$a_{\rm G}$   & GP covariance kernel amplitude & - & - & - \\
+$\ell$   & GP covariance kernel scale length & - & - & - \\
+\hline
+\end{tabular}
+
+~\clearpage
+
+\section{Discussion}\label{sec:discussion}
 
@@
 The raw spectrum of S68N shows H$_2$ emission lines indicative of either shocked material or accretion.
-Higher spectral resolution observations of protostars have shown CO emission \texttt{cite- seokho lee, etc.}.
+Higher spectral resolution observations of protostars have shown CO emission \citep{2016ApJ...826..179L}.
 With our NIRSPEC observations alone, it is impossible to assess whether CO emission partially fills in the CO lines at $2.3-2.4 \;\mu$m.
-Such line veiling would tend to reduce the equivalent widths of the CO lines, and bias our accretion-free estimate towards either \emph{higher} surface gravity or \emph{higher} veiling.
+Such line veiling would tend to reduce the equivalent widths of the CO lines, and bias our presumed accretion-free estimate towards either \emph{higher} surface gravity or \emph{higher} veiling.
 In other words, the ``true'' surface gravity and veiling is lower than our posterior would suggest.
@@
 We have assumed the disk radiates as a black body of a single temperature.
-More accurate estimates for the disk emission and geometries could be obtained from rigorous radiative transfer methods \citep[\emph{e.g.}]{2017arXiv170305765R}; no such advanced disk modeling was attempted.
+More accurate estimates for the disk emission and geometries could be obtained from rigorous radiative transfer methods \citep[][\emph{e.g.}]{2017arXiv170305765R}; no such advanced disk modeling was attempted.
 The relatively narrow $K-$ observation band does not offer a large enough lever arm to distinguish the nearly degenerate effects of elevated disk temperature versus increased solid angle of emission.
@@
 
-Below is a simulated spectrum of S68N with the JWST NIRSPEC IFU with the G235M grating providing $R\sim1000$ across $1.7-3.0 \; \mu$m, with a $S/N \sim 100$ per pixel.
+Below is a simulated spectrum of S68N with the JWST NIRSpec IFU with the G235M grating providing $R\sim1000$ across $1.7-3.0 \; \mu$m, with a $S/N \sim 100$ per pixel.
 

### 2017-05-24 sf/exp13/output/bb_absolute/run02/user_prior.py
Experiment 13, run 02-- config files and emcee output

@@ -1,0 +1,26 @@
+def user_defined_lnprior(p):
+    '''
+    Takes a vector of stellar parameters and returns the ln prior.
+    '''
+    if not ( (p[2] < 0.5) and (p[2] > 0) and
+             (p[3] < 1000.0) and (p[3] > -1000.0) and
+             (p[4] < 30) and (p[4] > -30) and
+             (p[6] < 1500.0) and (p[6] > 1000.0) and
+             (p[8] < 20.0) and (p[8] > 0.0) and
+             (p[9] < -1.7) and (p[9] > -2) and
+             (p[13] > 0.0) and (p[13] < 2.0) and
+             (p[14] < -1.0) and (p[14] > -3.0) and
+             (p[15] > 0.0) and (p[15] < 300 ) ):
+
+    	return -np.inf
+    
+    # Solar metalicity to within +/- 0.05 dex
+    lnp_FeH = -1.0*(p[2] - 0.01)**2/(2.0*0.001**2)
+    lnp_vz = -1.0*(p[3] - 0.0)**2/(2.0*20.0**2)
+    lnp_l = -1.0*(p[15] - 124.4)**2/(2.0*10.0**2)
+    lnp_logAmp = -1.0*(p[14] + 1.40)**2/(2.0*0.03**2)
+    # No prior on v_z.
+    ln_prior_out = lnp_FeH + lnp_vz + lnp_l + lnp_logAmp
+
+    return ln_prior_out
+

### 2017-05-30 document/ms.tex
Update MS includes info on SMM1

@@
 
+\subsection{SMM1}
+We also performed spectral inference on the source SMM1, a less embedded protostar showing less-conspicuous CO lines in its NIRSPEC $K-$band spectrum.
+The conditions of the inference we identical to those of S68N, namely the same stellar and nuissance parameter ranges and priors.
+We ran the MCMC sampling for a total of 20000 steps, discarding the first 15000 as burn-in.
+Figure \ref{fig:SMM1_spectrum} shows the spectrum of SMM1 with a model spectrum possessing parameters randomly chosen from its posterior samples.
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.85\columnwidth]{figures/SMM1_spectrum.pdf}
+ \caption{Observed and modeled spectrum of SMM1 with residual noise spectrum.}
+ \label{fig:SMM1_spectrum}
+\end{figure}
+
 %Table
@@
 $\logg$   & Surface gravity & 2 & 3 & 4 \\
-$\Z$   & Metallicity & - & - & - \\
 $v_r$   & Velocity error & - & - & - \\
